### 2023-10-16 2.State/rnn.tex
Done with vanishing gradient for now

The Vanishing gradient problem is a problem that comes when dealing with time depedent data \cite{vanishGrad}. When long amount of time depedent data is fed to the \ac{RNN}, the older the data, the lower the impact on the weight change. This phenomenen makes the \ac{RNN} less effective when it comes to very long time series.

>>>>

The Vanishing gradient problem is a problem that comes when dealing with time depedent data \cite{vanishGrad}. When big amount of time depedent data is fed to the \ac{RNN}, the weights can't be updated properly. The older the data, the lower it will impact how much the weight must change. Rendering the old input data almost useless. Classic \acp{RNN} must be used with relatively short time series.

Some \acp{RNN} were designed around this issue. This is the case of the \ac{LSTM} and \ac{GRU} which were created with internal mechanisms to regulate the flow of information and gradients.
